%2multibyte Version: 5.50.0.2960 CodePage: 65001
%\input{tcilatex}
%\input{tcilatex}


\documentclass[notitlepage,12pt]{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{amsfonts}
\usepackage{amsmath}

\setcounter{MaxMatrixCols}{10}
%TCIDATA{OutputFilter=LATEX.DLL}
%TCIDATA{Version=5.00.0.2552}
%TCIDATA{Codepage=65001}
%TCIDATA{<META NAME="SaveForMode" CONTENT="1">}
%TCIDATA{Created=Tuesday, November 13, 2012 12:43:14}
%TCIDATA{LastRevised=Wednesday, July 26, 2017 14:05:19}
%TCIDATA{<META NAME="GraphicsSave" CONTENT="32">}
%TCIDATA{<META NAME="DocumentShell" CONTENT="Standard LaTeX\Standard LaTeX Article">}
%TCIDATA{Language=American English}
%TCIDATA{CSTFile=40 LaTeX article.cst}

\newtheorem{theorem}{Theorem}
\newtheorem{acknowledgement}[theorem]{Acknowledgement}
\newtheorem{algorithm}[theorem]{Algorithm}
\newtheorem{axiom}[theorem]{Axiom}
\newtheorem{case}[theorem]{Case}
\newtheorem{claim}[theorem]{Claim}
\newtheorem{conclusion}[theorem]{Conclusion}
\newtheorem{condition}[theorem]{Condition}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{criterion}[theorem]{Criterion}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}
\newtheorem{exercise}[theorem]{Exercise}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{notation}[theorem]{Notation}
\newtheorem{problem}[theorem]{Problem}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{solution}[theorem]{Solution}
\newtheorem{summary}[theorem]{Summary}
\newenvironment{proof}[1][Proof]{\noindent\textbf{#1.} }{\ \rule{0.5em}{0.5em}}
\input{tcilatex}

\begin{document}

\title{Competitiveness and Carbon Taxes}
\author{Kortum and Weisbach \\
%EndAName
Yale and University of Chicago}
\maketitle

\begin{abstract}
Blah blah blah
\end{abstract}

\section{Leakage}

We focus on the case of $\eta =1$, in which energy is consumed only
indirectly through consumption of manufactures. In that case emissions show
up as: $M_{e}^{HH}$, $M_{e}^{FH}$, $M_{e}^{HF}$, and $M_{e}^{FF}$ (the first
subscript is the point of consumption and the second the point of
production). In a baseline of no carbon taxes, the fraction of emissions due
to \emph{production} in $\mathcal{F}$ is:%
\begin{eqnarray*}
\frac{M_{e}^{HF}+M_{e}^{FF}}{M_{e}^{HH}+M_{e}^{FH}+M_{e}^{HF}+M_{e}^{FF}} &=&%
\frac{p_{e}M_{e}^{HF}+p_{e}M_{e}^{FF}}{%
p_{e}M_{e}^{HH}+p_{e}M_{e}^{FH}+p_{e}M_{e}^{HF}+p_{e}M_{e}^{FF}} \\
&=&\frac{\left( 1-\gamma \right) \left( 1-\bar{j}\right) \left( \pi
_{c}Y+\pi _{c}^{\ast }Y^{\ast }\right) }{\left( 1-\gamma \right) \left( \pi
_{c}Y+\pi _{c}^{\ast }Y^{\ast }\right) } \\
&=&1-\bar{j},
\end{eqnarray*}%
where $\bar{j}$ is $\mathcal{H}$'s market share in tradable manufactures.
The fraction of emissions due to \emph{consumption} in $\mathcal{F}$ is:%
\begin{equation*}
\frac{M_{e}^{FH}+M_{e}^{FF}}{M_{e}^{HH}+M_{e}^{FH}+M_{e}^{HF}+M_{e}^{FF}}=%
\frac{\left( 1-\gamma \right) \pi _{c}^{\ast }Y^{\ast }}{\left( 1-\gamma
\right) \left( \pi _{c}Y+\pi _{c}^{\ast }Y^{\ast }\right) }=1-\omega _{c},
\end{equation*}%
where%
\begin{equation*}
\omega _{c}=\frac{\pi _{c}Y}{\pi _{c}Y+\pi _{c}^{\ast }Y^{\ast }}
\end{equation*}%
is $\mathcal{H}$'s share of world spending on the $c$-good.

We define \emph{modified leakage} $\tilde{l}_{P}$ as the increased emissions
in $\mathcal{F}$ resulting from a unilateral carbon tax in $\mathcal{H}$
relative to the resulting decline in global emissions. A value of $\tilde{l}%
_{P}>0$ means that $\mathcal{F}$ has increased its emissions even as global
emissions have declined due to the carbon tax in $\mathcal{H}$. Recall that
the proportional change in global emissions is denoted by $G$ (so that for
any carbon tax worth considering, we can take $G<1$). Our leakage formula is
thus:%
\begin{eqnarray*}
\tilde{l}_{P} &=&\frac{\left( M_{e}^{HF^{\prime }}+M_{e}^{FF^{\prime
}}\right) -\left( M_{e}^{HF}+M_{e}^{FF}\right) }{\left(
M_{e}^{HH}+M_{e}^{FH}+M_{e}^{HF}+M_{e}^{FF}\right) \left( 1-G\right) } \\
&=&\frac{1}{1-G}\frac{M_{e}^{HF}\left( \hat{M}_{e}^{HF}-1\right)
+M_{e}^{FF}\left( \hat{M}_{e}^{FF}-1\right) }{%
M_{e}^{HH}+M_{e}^{FH}+M_{e}^{HF}+M_{e}^{FF}} \\
&=&\frac{1-\bar{j}}{1-G}\left( \omega _{c}\hat{M}_{e}^{HF}+\left( 1-\omega
_{c}\right) \hat{M}_{e}^{FF}-1\right) .
\end{eqnarray*}%
It is driven by the proportional increase in $\mathcal{F}$'s use of energy
in manufactures produced for its export market and in manufactures produced
for its home market. To derive expressions for these changes, we need to
take a stand on the specific carbon taxes being considered.

We treat the carbon tax in $\mathcal{H}$ as a combination of a production
tax $t_{p}^{\prime }$ and a border tax adjustment $t_{b}^{\prime }\in
\lbrack 0,t_{p}^{\prime }]$. With no border adjustments ($t_{b}^{\prime }=0$%
) it is a pure production tax (at rate $t_{p}^{\prime }$) while with full
border adjustments ($t_{b}^{\prime }=t_{p}^{\prime }$) it is a pure
consumption tax (at rate $t_{b}^{\prime }$). The reduction in global
emissions $G$ under such policies is acheived through reduced demand for
energy, which drives down the price of energy faced by the extraction
sector, leading that sector to supply less energy on the world market. This
reduction in the price of energy $\hat{p}_{e}$, known as the \emph{fuel
price effect}, is connected to the reduction in global emissions via the
energy supply curve:%
\begin{equation}
\hat{p}_{e}=G^{(1-\beta )/\beta }.  \label{fuel price effect}
\end{equation}

The effect of such policies on changes in production in $\mathcal{F}$ are
given by:%
\begin{equation*}
\hat{M}_{e}^{HF}=\frac{1-\bar{j}^{\prime }}{1-\bar{j}}\frac{\hat{\pi}_{c}%
\hat{Y}}{\left( 1+t_{b}^{\prime }\right) \hat{p}_{e}}
\end{equation*}%
and%
\begin{equation*}
\hat{M}_{e}^{FF}=\frac{1-\bar{j}^{\prime }}{1-\bar{j}}\frac{\hat{\pi}%
_{c}^{\ast }\hat{Y}^{\ast }}{\hat{p}_{e}}.
\end{equation*}%
Plugging these expressions into the leakage formula:%
\begin{equation*}
\tilde{l}_{P}=\frac{1-\bar{j}}{1-G}\left( \frac{1-\bar{j}^{\prime }}{1-\bar{j%
}}\left[ \omega _{c}\hat{\pi}_{c}\hat{Y}/\left( 1+t_{b}^{\prime }\right)
+\left( 1-\omega _{c}\right) \hat{\pi}_{c}^{\ast }\hat{Y}^{\ast }\right] 
\frac{1}{\hat{p}_{e}}-1\right) 
\end{equation*}%
Leakage is driven by three basic factors: (i) the trade share effect is the
change in $\mathcal{F}$'s market share in manufacturing $\left( 1-\bar{j}%
^{\prime }\right) /\left( 1-\bar{j}\right) $, (ii) the fuel price effect is
the inverse of the proportional decline in the global energy price $1/\hat{p}%
_{e}$, and (iii) the spending effect is the change in world spending on
manufactured goods (taking account of any border tax adjustment) $\omega _{c}%
\hat{\pi}_{c}\hat{Y}/\left( 1+t_{b}^{\prime }\right) +\left( 1-\omega
_{c}\right) \hat{\pi}_{c}^{\ast }\hat{Y}^{\ast }$. We can consider these
factor separately.

The trade share effect is the change in $\mathcal{F}$'s market share in
manufactures, given by:%
\begin{equation*}
\frac{1-\bar{j}^{\prime }}{1-\bar{j}}=\frac{1}{\bar{j}\left( \frac{%
1+t_{p}^{\prime }}{1+t_{b}^{\prime }}\right) ^{-\theta \left( 1-\gamma
\right) }+1-\bar{j}}.
\end{equation*}%
This factor is increasing in the effective production tax rate $\tilde{t}%
_{p}^{\prime }$, defined by $1+\tilde{t}_{p}^{\prime }=(1+t_{p}^{\prime
})/(1+t_{b}^{\prime })$, which shifts production from $\mathcal{H}$ to $%
\mathcal{F}$. With full border tax adjustments this factor reduces to $1$
and no longer contributes to leakage.

The second factor is the fuel price effect. If a carbon tax leads to a
reduction in global emissions, equation (\ref{fuel price effect}) tells us
there will be a reduction in the energy price. Since this change is in the
denominator, the fuel price effect always contributes positively to leakage.
For a given change in spending on manufactures (and hence on energy), it
implies a greater increase in energy use. But, unlike the trade share
effect, the fuel price effect leads to greater energy use in both countries.

The third factor is the most nuanced. There are declines in income in both
countries due to reduced rents from energy deposits. There are increases in
income in $\mathcal{H}$ due to new tax revenue. There are also changes in
the share of income spent on manufactures, due to price changes and taxes.
Consider the change in the share of income spent on the manufactured good in 
$\mathcal{H}$:%
\begin{equation*}
\hat{\pi}_{c}=\frac{\hat{p}_{c}^{-\left( \sigma -1\right) }}{\pi _{c}\hat{p}%
_{c}^{-\left( \sigma -1\right) }+1-\pi _{c}}
\end{equation*}%
and likewise for $\mathcal{F}$. Changes in these shares depend on changes in
the price of the manufactured good. In $\mathcal{H}$ that change is given by:%
\begin{eqnarray*}
\hat{p}_{c} &=&\hat{p}_{m}=\hat{p}_{e}^{1-\gamma }\left( \bar{j}\left(
1+t_{p}^{\prime }\right) ^{-\theta \left( 1-\gamma \right) }+\left( 1-\bar{j}%
\right) \left( 1+t_{b}^{\prime }\right) ^{-\theta \left( 1-\gamma \right)
}\right) ^{-1/\theta } \\
&=&\left( 1+t_{b}^{\prime }\right) ^{\left( 1-\gamma \right) }\hat{p}%
_{e}^{1-\gamma }\left( \bar{j}\left( \frac{1+t_{p}^{\prime }}{%
1+t_{b}^{\prime }}\right) ^{-\theta \left( 1-\gamma \right) }+\left( 1-\bar{j%
}\right) \right) ^{-1/\theta },
\end{eqnarray*}%
while in $H$:%
\begin{equation*}
\hat{p}_{c}^{\ast }=\hat{p}_{e}^{1-\gamma }\left( \bar{j}\left( \frac{%
1+t_{p}^{\prime }}{1+t_{b}^{\prime }}\right) ^{-\theta \left( 1-\gamma
\right) }+\left( 1-\bar{j}\right) \right) ^{-1/\theta }.
\end{equation*}%
The last term in each expression is the proportional increase in the price
of the manufactured good caused by the effective production tax, which
raises costs in $\mathcal{H}$ and leads to a change in the goods that each
country specializes in. The fuel price effect partially offsets this price
increase. Only the border tax adjustment causes prices to rise more in $%
\mathcal{H}$ than in $\mathcal{F}$:%
\begin{equation*}
\frac{\hat{p}_{c}}{\hat{p}_{c}^{\ast }}=\left( 1+t_{b}^{\prime }\right)
^{\left( 1-\gamma \right) }.
\end{equation*}%
To understand these three factors more clearly, it is helpful to consider
two special cases.

\subsection{Pure Production Tax}

In the case of a pure production tax ($t_{b}^{\prime }=0$), these price
changes would be the same. If the initial shares were the same ($\pi
_{c}=\pi _{c}^{\ast }$) then changes in shares would be the same $\hat{\pi}%
_{c}=\hat{\pi}_{c}^{\ast }$. In this case leakage is simply:%
\begin{eqnarray*}
l_{P} &=&\hat{\pi}_{c}\frac{\omega _{c}\hat{Y}+\left( 1-\omega _{c}\right) 
\hat{Y}^{\ast }}{\bar{j}\left( \frac{1+t_{p}^{\prime }}{1+t_{b}^{\prime }}%
\right) ^{-\theta \left( 1-\gamma \right) }+1-\bar{j}}G^{-1/\beta } \\
&=&
\end{eqnarray*}

\begin{equation*}
\tilde{l}_{P}=\frac{1-\bar{j}}{1-G}\left( \frac{1-\bar{j}^{\prime }}{1-\bar{j%
}}\left[ \omega _{c}\hat{\pi}_{c}\hat{Y}/\left( 1+t_{b}^{\prime }\right)
+\left( 1-\omega _{c}\right) \hat{\pi}_{c}^{\ast }\hat{Y}^{\ast }\right] 
\frac{1}{\hat{p}_{e}}-1\right) 
\end{equation*}

\subsection{Pure Consumption Tax}

In the case of a pure consumption tax ($t_{b}^{\prime }=t_{p}^{\prime }$),
there is no change in $F$'s trade share:%
\begin{equation*}
\frac{1-\bar{j}^{\prime }}{1-\bar{j}}=\frac{1}{\bar{j}+1-\bar{j}}=1.
\end{equation*}%
Thus leakage is due only to the increase in foreign consumption brou%
\begin{equation*}
l_{P}=\left( \omega _{c}\hat{\pi}_{c}\hat{Y}+\left( 1-\omega _{c}\right) 
\hat{\pi}_{c}^{\ast }\hat{Y}^{\ast }\right) G^{-1/\beta }
\end{equation*}

\end{document}
